---
title: "GDP MLR Model"
author: "Rishi Sarraff, Navya Aenugu, Avery Brazelton, Isabella Barton"
fontsize: 12pt
output:
  pdf_document: default
  html_document:
    df_print: paged
urlcolor: black
geometry: margin=1in
header-includes:
- \usepackage{setspace}
- \onehalfspacing
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, highlight=FALSE, comment=NA, warnings=FALSE,message=FALSE)
```

## Introduction

## Methods and Analysis
  The data used for this project contained country-level information across 165 nations on multiple quantitative and categorical factors such as life expectancy, dependency, growth, income, and more. The target variable for prediction modeling was the log-transformed version of the GDP per capita calculated in US Dollars.
Before analyzing and conducting tests on the data. We spent time cleaning the data by filtering out NA values, replacing NA values with sources from the same database, converting the structures of the objects, and reformatting the position and ordering for easier access. 
  
  First, we conducted an initial exploratory analysis by plotting all quantitative variables with GDP on scatterplots to understand the relationships between these variables and GDP. We analyzed qualitative factors like country size, income level, and growth rate with boxplots and interaction plots. Multicollinearity and variable screening through stepwise regression helped identify highly correlated predictor variables; we determined the removal and addition of quantitative predictors such as fertility and dependency through variable screening played a pivotal role in increasing model accuracy.
  
  The remaining significant quantitative predictors that remained after these steps were average age, life expectancy, and their interaction. After we tested different combinations of qualitative factors like income level, size, and growth rate, and through comparison of model fit statistics we only included income since the other proved not to be significant. The final selected model contained average age, life expectancy, their interaction, and income level classified into four categories or three dummy variables (high income, low income, lower middle income, upper middle income). We ensured that the best model was chosen through a Global F test, a Nested F Test on the income levels, t-tests on important predictors, R^2 values, and 2s values.   
  
  This linear regression model was then tested for violations of assumptions through residual analysis split into residual plots, influence analysis, and outlier detection. Through the residual plots, we confirmed that the zero mean and constant variance assumptions were not violated. From the Q-Q plot and Histogram, we confirmed that the normality assumption was not violated. However, after careful analysis of the influential observations, we noticed five influential points that can be categorized as outliers due to their influence on the data. These countries were 4(Angola), 128(San Marino), 133(Seychelles), 134(Sierra Leone), 156(Ukraine). Through influence plots such as the cook's distance, studentized residuals, and leverage, we used a subsetting technique to confirm that the removal of these data points sharpened the model by increasing the R2 and F Statistics, reducing the residual standard error, and P-value.
    
  As an additional means of relevant analysis, we learned about the box-cox analysis method and applied a box-cox transformation to check sensitivity to transformations. From this, we learned that the log transformation applied to the GDP was significant and played a crucial role in accurately linearizing the data necessary for analysis.
Finally, we concluded that our model was adequate with an R2 of 0.8733, meaning 87.33% of the variability observed in GDP per capita is explained by the regression model. Comparing this to the first most model with an R2 of 0.6393 and the pre-residual analysis model with an R2 of 0.7396, our latest and final model accounts for the best parameters and fits our data. From this, we used our model for estimation and prediction and calculated the confidence and prediction intervals for E(y) and y, respectively. Using data within our frame, we accurately predicted multiple parameters such as the GDP, Average Age, and more of a country given values using 95% confidence.


## Results

## Conclusions


\newpage
\begin{center}
  \Huge\textbf{Data Cleaning and Processing}
\end{center}

```{r}
## we will use MLR since our response variable is not binary in its outcomes 
## of success or failure
library(ggplot2)
library(dplyr)
library(corrplot)
library(Hmisc)
library(car)
library(olsrr)
library(MASS)

data <- read.csv("/Users/sarra/Documents/UVA/Second Year/Fall 2023/Stat 3220/Project/Stat3220dataset.csv")


## Here we replace any N/A values with the average of the other values if 
## quantitative and the base case if qualitative, so no harm is done through
## assumption.

data <- na.omit(data)

data$Growth[39] <- "A" 
#https://data.worldbank.org/country/CY

data$Average.Age[159] <- 38.5 
# https://www.cia.gov/the-world-factbook/field/median-age/country-comparison/

## data Pre-processing, converting from different types to expected types
data$Total.Population <- gsub(",", "", data$Total.Population)
## changing population from char to numeric
data$Total.Population <- as.numeric(data$Total.Population) 

data$Density <- gsub(",", "", data$Density)
## changing density from char to numeric
data$Density <- as.numeric(data$Density) 
## changing averageAge from int to double 
data$Average.Age <- as.numeric(data$Average.Age) 



data$GDP <- log(data$GDP) 
## converted the response variable to log, so histogram works.
data$Average.Age <- log(data$Average.Age)


## Histogram:
## this needs some serious refitting and transformations of the variables.
ggplot(data, aes(x = GDP)) +
  geom_histogram(bins = round(sqrt(165)), fill = "blue", color = "black") + 
  labs(title = "Histogram of Response Variable - GDP", x = "GDP", y = "Frequency")

## After transforming data using log function, we have histogram that is
## unimodal, mostly symmetrical, continuous, and very few outliers recommended
## by R itself, was 13 as the number of bins, so we kept it as the rounding of
## the square root of the number of data points.

## Reordering data for easier calling:

numeric_vars <- c("Name", "Total.Population", "Growth.Rate..Value.", "Density",
                  "Fertility", "Life_Expectancy", "Under.5.Mortality.Rate", 
                  "Sex_Ratio", "Dependency", "Average.Age", "Debt")
categorical_vars <- c("Size", "Growth", "Income", "GDP")

 ## converting the categorical data from characters to factors
for(i in categorical_vars[1:3]){
  data[[i]] <- as.factor(data[[i]])
}

data <- data %>% dplyr:: select(all_of(numeric_vars), all_of(categorical_vars))
```



\newpage

\begin{center}
  \Huge\textbf{Exploratory Data Analysis}
\end{center}

```{r}
## 1st step after transformations is to do some EDA:

## Quantitative x Quantitative SCATTERPLOTS
for (i in names(data)[2:11]) {
  plot(data[, i], data$GDP, xlab = i, ylab = "GDP", 
  main = paste("The Relationship between GDP and", i))
  print(cor(data[[i]], data$GDP, use = "complete.obs"))
}

## Qualitative x Qualitative BOXPLOTS

for (i in names(data)[12:14]) {
  boxPlot <- ggplot(data, aes_string(x=i, y="GDP")) + geom_boxplot(fill="red", color = "black")+ scale_fill_brewer(palette = "Set1") + labs(x=i, y = "GDP",title = paste("The Relationship between GDP and", i)) +theme(plot.title = element_text(hjust = 0.5))
      
  print(tapply(data$GDP, data[[i]], summary))

  print(boxPlot)

}



## Interaction Plots for Qualitative X Qualitative

## for Size and Growth
interaction.plot(data$Size, data$Growth, data$GDP,fun=mean, 
                 trace.label="Growth", xlab="Size",ylab="GDP")

table(data$Size,data$Growth)


## for Growth and Income
interaction.plot(data$Growth, data$Income, data$GDP,fun=mean,
                 trace.label="Income", xlab="Growth",ylab="GDP")

table(data$Growth,data$Income)


## for Size and Income
interaction.plot(data$Income, data$Size, data$GDP,fun=mean,
                 trace.label="Size", xlab="Income",ylab="GDP")

table(data$Size,data$Income)


## Interaction Plots for Qualitative X Quantitative:

# Total Population x Size, Income, Growth
plot(GDP~Total.Population , col=factor(Size),data=data,
     xlab="Total Population",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Size)),
       pch = 19,
       col = factor(levels(factor(data$Size))))

plot(GDP~Total.Population , col=factor(Income),data=data,
     xlab="Total Population",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Income)),
       pch = 19,
       col = factor(levels(factor(data$Income))))
plot(GDP~Total.Population , col=factor(Growth),data=data,
     xlab="Total Population",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Growth)),
       pch = 19,
       col = factor(levels(factor(data$Growth))))

# Under 5 Mortality Rate x Size, Income, Growth
plot(GDP~Under.5.Mortality.Rate , col=factor(Size),data=data,
     xlab="Under 5 Mortality Rate",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Size)),
       pch = 19,
       col = factor(levels(factor(data$Size))))

plot(GDP~Under.5.Mortality.Rate , col=factor(Income),data=data,
     xlab="Under 5 Mortality Rate",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Income)),
       pch = 19,
       col = factor(levels(factor(data$Income))))

plot(GDP~Under.5.Mortality.Rate , col=factor(Growth),data=data,
     xlab="Under 5 Mortality Rate",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Growth)),
       pch = 19,
       col = factor(levels(factor(data$Growth))))


# Sex Ratio x Size, Income, Growth
plot(GDP~Sex_Ratio , col=factor(Size),data=data,xlab="Sex Ratio",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Size)),
       pch = 19,
       col = factor(levels(factor(data$Size))))

plot(GDP~Sex_Ratio , col=factor(Income),data=data,xlab="Sex Ratio",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Income)),
       pch = 19,
       col = factor(levels(factor(data$Income))))

plot(GDP~Sex_Ratio , col=factor(Growth),data=data,xlab="Sex Ratio",ylab="GDP") 
legend("topright",
       legend = levels(factor(data$Growth)),
       pch = 19,
       col = factor(levels(factor(data$Growth))))


```
\newpage

\begin{center}
  \Huge\textbf{Multicollinearity and Variable Screening}
\end{center}
```{r}
## Since we have more than 10 explanatory variables, we will run 
## multicollinearity tests on the quantitative variables:


## we will perform an analysis on the pairwise relations and then use Stepwise 
## regression as a variable screening technique
gdpCorr <- round(cor(data[2:10], use = "complete.obs"), 3)
gdpCorr

corrplot(gdpCorr)

## From this we can see that there are a few pairwise relations that are of concern:
  ## 1. Life_Expectancy and Under 5 Mortality Rate --> -0.884
  ## 2. Fertility and Growth Rate Value --> 0.860
  ## 3. Fertility and Average Age --> -0.855
  ## 4. Fertility and Dependency --> 0.859
  ## 5. Average Age and Growth Rate Value --> 0.806

## We will now run a model for VIF and test for multicollinearity

multiModel <- lm(GDP ~. -Name -Size - Growth -Income, data = data)
multiModel

summary(multiModel)

multiModelVIF <- round(vif(multiModel), 3)
multiModelVIF

mean(multiModelVIF)

## the average VIF appears to be 7.8822, which is much higher than the 3 cutoff
## and there are a few quantitative factors that have an individual VIF higher
## than 10 such as Fertility, Dependency, and Average Age. This is enough 
## evidence for us to run step_wise regression and eliminate some quantitative 
## variables.

## Variable Screening: 

ols_step_both_p(multiModel, pent=0.15, prem=0.15, details=F)
ols_step_forward_p(multiModel, pent = 0.15, prem= 0.15, details = F)
ols_step_backward_p(multiModel, pent = 0.15, prem = 0.15, details = F)

## After stepwise regression, we see that the remaining values are Life 
## Expectancy, Sex Ratio, and Average Age. We will now confirm that these 
## combinations still yield a unconcerning multicollinearity value, removing 
## dependency and fertility, which caused most of the multicollinearity, yields 
## a viable equation.

multiModel2 <- lm(GDP ~. -Name -Size - Growth -Income -Fertility -Density 
                  -Growth.Rate..Value. -Total.Population -Under.5.Mortality.Rate
                  -Debt -Dependency, data = data)
multiModel2

summary(multiModel2)

multiModelVIF2 <- round(vif(multiModel2), 3)
multiModelVIF2

mean(multiModelVIF2) # 2.517

```

```{r}
## Finalize Quantitative Relationships


## Let's look at Quantitative x Quantitative Interactions
interactionModel <- lm(GDP ~. -Name -Size - Growth -Income -Fertility -Density 
                      -Growth.Rate..Value. -Total.Population -Under.5.Mortality.Rate
                      -Debt -Dependency + Average.Age*Life_Expectancy, data = data)

summary(interactionModel) ## comparing this to multimodel, it seems that average
                          ## age and life expectancy is significant
s2interaction <- summary(interactionModel)$sigma^2
s2interaction


## therefore, we can retain the old model as our best model and move onto the 
## qualitative predictors.
preQualModel <- lm(GDP ~ Average.Age + Life_Expectancy + Sex_Ratio + 
                     Average.Age*Life_Expectancy, data = data)
summary(preQualModel)
s2 <- summary(preQualModel)$sigma^2
s2

## Global F test and T tests for each of the predictors, prove that this is an 
## adequate model with valid predictors

```
\newpage

\begin{center}
  \Huge\textbf{Adding Qualitative Variables and Fitting Linear Models}
\end{center}

```{r}
## Qualitative Addition to current model
## look at the interaction plots from the EDA and decide to add 
## and modify from there.

## Looking at the boxplots, all three of the quantitative variables seem
## to have a relationship with GDP, looking further into this through 
## the interaction plots:

## 1) For the Qualitative x Qualitative interaction plots, it appears that
## there are 2 interactions that are relevant in the EDA:
     # a) Size x Growth
     # b) Growth x Income

## 2) For the Qualitative x Quantitative interaction plots, 
## it appears that there ## is 1 interaction that is relevant in the EDA:
     # a) Sex_Ratio x Income

testModel1 <- lm(GDP ~ Size + Income + Growth, data = data)
summary(testModel1) ## Only income is significant in this model, so size and 
## growth can be removed
s2_one <- summary(testModel1)$sigma^2
s2_one

testModel2 <- lm(GDP ~ Average.Age  + Sex_Ratio + Life_Expectancy + 
                  Average.Age*Life_Expectancy + Income, data = data)
summary(testModel2) ## shows that sex_ratio is no longer valid 
s2_two <- summary(testModel2)$sigma^2
s2_two

eYModel <- lm(GDP ~ Average.Age + Life_Expectancy + Average.Age*Life_Expectancy
              + Income, data = data)
summary(eYModel)
s2_three <- summary(eYModel)$sigma^2
s2_three

## As shown below, the multiple R-squared value is highest for the E(y) model, 
## and the 2s value is the lowest for this model, making it the final model
## , or best model for choice
```
After analysis and multiple levels of filtering data, the best model currently has the estimation and prediction equations of :

$log(E(GDP))=\beta_0+\beta_1log(AverageAge)+\beta_2 Life Expectancy+\beta_3 log(Average Age)*Life Expectancy + \beta_4 Low Income+ \beta_5 Lower Middle Income+\beta_6 Upper Middle Income$

$log(\widehat{GDP}) =  25.5994 - 5.7567 log(AverageAge)-0.2256 Life Expectancy+ 0.0812 log(Average Age)*Life Expectancy - 2.7566 Low Income - 1.7548 Lower Middle Income - 0.8700 Upper Middle Income$

Where:

  •  Low Income = 1 if Country is classified as Low Income, 0 otherwise
  
  •  Lower Middle Income = 1 if Country is classified as Lower Middle Income, 0 otherwise
  
  •  Upper Middle Income = 1 if Country is classified as Upper Middle Income, 0 otherwise
  
  •  Base Case: High Income = 0
  
  
Interpretation of Our Response Variable: 

  • The GDP is measured as the GDP per capita in US Dollars which represents the average economic output per person in a certain country and this can be calculated using the GDP of the country/population. We transformed this GDP per capita value using a log transformation, so it can be interpreted as the log of the GDP per capita in USD that increases or decreases depending on the values of the predictors.
  

**Global F test** *Look below at residual analysis section for Finalized Model*

-   *Hypotheses*:
    -   $H_0: \beta_1= \beta_2=\beta_3=\beta_4 = \beta_5 = \beta_6 =0$ (the model is not adequate)
    
    -   $H_a$:at least one of $\beta_1 , \beta_2 , \beta_3,\beta_4, \beta_5, \beta_6 \neq 0$ (the model is adequate)
    
-   *Distribution of test statistic*: F with 6, 158 DF

-   *Test Statistic*: F=74.79

-   *Pvalue*: \<2.2e-16

-   *Decision*: 2.2e-16\<0.05 -\> REJECT H0

-   *Conclusion*: The model with Average age, life expectancy, interaction between average age and life expectancy, and the 4 levels of Income(Low income, lower middle income, upper middle income, and high income) proves to be significant and rejects the null hypothesis, so we would use this model as of now before we determine a better model through further analysis.


**T-Tests for Individual Predictors**

-  *Hypotheses*:

    -   $H_0: \beta_1=0$ (Average Age does NOT contribute to predicting country GDP)
    
    -   $H_a:\beta_1 \neq 0$ (Average Age contributes to predicting country GDP)
    
-   *Test Statistic*: t=-2.002

-   *Pvalue*: \<0.03359

-   *Decision*: \<0.03359\<0.05 -\> REJECT H0

-   *Conclusion*: Average Age is significant in predicting Country GDP and rejects the null hypothesis.


-  *Hypotheses*:

    -   $H_0: \beta_2=0$ (Life Expectancy does NOT contribute to predicting country GDP)
    
    -   $H_a:\beta_2 \neq 0$ (Life Expectancy contributes to predicting country GDP)
    
-   *Test Statistic*: t=-1.784

-   *Pvalue*: \< 0.07634

-   *Decision*: \<0.07634\<0.1 -\> REJECT H0

-   *Conclusion*: Life Expectancy is significant in predicting Country GDP and rejects the null hypothesis.


-  *Hypotheses*:

    -   $H_0: \beta_3=0$ (The interaction between Average Age and Life Expectancy does NOT contribute to predicting country GDP)
    
    -   $H_a:\beta_3 \neq 0$ (The interaction between Average Age and Life Expectancy contributes to predicting country GDP)
    
-   *Test Statistic*: t= 2.110 

-   *Pvalue*: \< 0.03640 

-   *Decision*: \<0.03640 \<0.05 -\> REJECT H0

-   *Conclusion*: The interaction between Average Age and Life Expectancy is significant in predicting Country GDP and rejects the null hypothesis.


**Nested F test**
```{r}
  reducedModel <- lm(GDP ~ Average.Age + Life_Expectancy + 
                       Average.Age*Life_Expectancy, data = data)
  summary(reducedModel)
  anova(reducedModel, eYModel)
```
-  *Hypotheses*:
    -   $H_0: \beta_4\ and \beta_5\ and \beta_6=0$ (Income) does NOT contribute to predicting country GDP)
    -   $H_a: \beta_4\ and \beta_5\ and \beta_6 \neq 0$ (Income contributes to predicting country GDP)
    
-   *Test Statistic*: t=-8.033, -7.125, -4.372, respectively

-   *Pvalue*: \< 1.453e-12

-   *Decision*: \ 1.453e-12 < 0.05 -\> REJECT H0

-   *Conclusion*: The income is significant at predicting country GDP. We will keep all three dummy variables in the model and not test them individually since our model 2, which is the model with Income as a qualitative predictor is more significant compared to the other model without our income.


\newpage

\begin{center}
  \Huge\textbf{Residual Analysis}
\end{center}

```{r}
## Performing Residual Analysis to Check Assumptions for Violation:

residualPlots(eYModel, tests = F) ## for lack of fit, we dont have any violations

plot(eYModel, which = c(1,2)) ## Tests the unequal variance violation through a 
## Q-Q Plot, no violations, but there are some weird outliers

hist(residuals(eYModel), xlab = "Residuals", ylab = "Frequency", 
     main = "The Histogram of Residuals of our Quantitative Model")  
     ## Gives us a histogram to test normality --> our histogram is normal

## Performing Residual Analysis to Check Outliers and Influential Points:

influencePlot(eYModel, fill = F) 

plot(eYModel, which = 4)


## Influential Observation Analysis
dffits(eYModel)[c(4, 128, 133, 134, 156)] 
## here we get the dffits and dfbetas of the influential points to do further
## analysis.

dfbetas(eYModel)[c(4, 128, 133, 134, 156)]
mean(dffits(eYModel))

dim(data)

subdata <- data[-c(4, 128, 133, 134, 156),] 
## we would  remove these influential points since these specific ones cross our
## threshold and act as outliers in terms of fitting on the plots and all.


finalModel <- lm(GDP ~ Average.Age + Life_Expectancy + Average.Age*Life_Expectancy
                 + Income,  data = subdata)
summary(finalModel) ## model with removed influential has much better
                    ## fitting metrics compared to other model
s2_final <- summary(finalModel)$sigma^2
s2_final
## higher adjusted r squared, higher p-values, lower residual standard error,
## and higher F-Statistic.

## These outlier plots all show that 4 values or countries are outlier values: 
## 4(Angola), 128(San Marino), 133(Seychelles), 134(Sierra Leone), 156(Ukraine).
## To determine whther or not to remove these influential points, we extracted 
## the dffits and dfbetas values and comparing these, we found that all these 
## points vary by large amounts from the mean.
```
After readjusting the data points through residual analysis, here are the final model and prediction equations

$log(E(GDP))=\beta_0+\beta_1log(AverageAge)+\beta_2 Life Expectancy+\beta_3 log(Average Age)*Life Expectancy + \beta_4 Low Income+ \beta_5 Lower Middle Income+\beta_6 Upper Middle Income$

$log(\widehat{GDP}) =  23.3857 - 5.3241 log(AverageAge) - 0.1848 Life Expectancy + 0.0726 log(Average Age)*Life Expectancy - 3.0819 Low Income - 1.8835 Lower Middle Income - 0.9782 Upper Middle Income$

Where:

  •  Low Income = 1 if Country is classified as Low Income, 0 otherwise
  
  •  Lower Middle Income = 1 if Country is classified as Lower Middle Income, 0 otherwise
  
  •  Upper Middle Income = 1 if Country is classified as Upper Middle Income, 0 otherwise
  
  •  Base Case: High Income = 0
  

Interpretation of Our Response Variable and Explanatory Variables: 

  • The GDP is measured as the GDP per capita in US Dollars which represents the average economic output per person in a certain country and this can be calculated using the GDP of the country/population. We transformed this GDP per capita value using a log transformation, so it can be interpreted as the log of the GDP per capita in USD that increases or decreases depending on the values of the predictors.
  
  • Average Age: For every 1 unit increase in the log(Average Age), the log(GDP per Capita in USD) decreases -5.3241. The Average Age has units measured in years.
  
  • Life_Expectancy: For every 1 unit increase in the Life Expectancy, the log(GDP per Capita in USD) decreases -0.1848. The Life Expectancy has units measured in years.
  
  • Average Age*Life_Expectancy: For every 1 unit increase in the log(Average Age) x Life_Expectancy, the log(GDP per Capita in USD) increases 0.0726.
  
  • Low Income: If a country is classified as a low income country, the log(GDP per Capita in USD) decreases -3.0819.
  
  • Lower Middle Income: If a country is classified as a lower middle income country, the log(GDP per Capita in USD) decreases -1.8835.
  
  • Upper Middle Income: If a country is classified as a upper middle income country, the log(GDP per Capita in USD) decreases -0.9782.
  
  • High Income: If a country is classified as a High income country, the log(GDP per Capita in USD) does not decrease or increase.
  
  

**Global F test** *For the final model*

-   *Hypotheses*:
    -   $H_0: \beta_1= \beta_2=\beta_3=\beta_4 = \beta_5 = \beta_6 =0$ (the model is not adequate)
    -   $H_a$:at least one of $\beta_1 , \beta_2 , \beta_3,\beta_4, \beta_5, \beta_6 \neq 0$ (the model is adequate)
    
-   *Distribution of test statistic*: F with 6, 153 DF

-   *Test Statistic*: F=175.8

-   *Pvalue*: \<2.2e-16

-   *Decision*: 2.2e-16\<0.05 -\> REJECT H0

-   *Conclusion*: The model with Average age, life expectancy, interaction between average age and life expectancy, and the 4 levels of Income(Low income, lower middle income, upper middle income, and high income) proves to be significant and rejects the null hypothesis, so we would use this model. Assessing and comparing this model with the older model, we can figure out that this model has a higher R-Squared, adjusted R-Squared, F-statistic, and lower residual standard error. Moreover, looking at the 2s value of this model, we also see that it has a lower sigma squared value of 0.2716 in comparison to the older eYModel, which has a sigma squared value of 0.3943.

Future Question: To what extent and what features of the analysis would change if different variables of the data were to be changed using different transformation techniques?

\newpage

\begin{center}
  \Huge\textbf{Box Cox Transformation}
\end{center}

```{r}
## Box Cox Transformation
set.seed(123)
train_index <- sample(1:nrow(data), 0.8*nrow(data))  
train_data <- data[train_index,]
test_data <- data[-train_index,]

boxcox_trans <- boxcox(eYModel) 
lambda <- boxcox_trans$x[which.max(boxcox_trans$y)]
train_data$GDP_bc <- (train_data$GDP^lambda - 1)/lambda  

eYModel_bc <- lm(GDP_bc ~ Average.Age + Life_Expectancy + 
                   Average.Age*Life_Expectancy + Income,
                 data = train_data)

test_data$GDP_bc <- (test_data$GDP^lambda - 1)/lambda 
predictions <- predict(eYModel_bc, newdata = test_data)

test_MSE <- mean((test_data$GDP_bc - predictions)^2)
print(test_MSE)

```

\newpage

\begin{center}
  \Huge\textbf{Confidence and Prediction Intervals}
\end{center}

```{r}
# We can therefore, employ this new and final model for estimation and 
## prediction using the metrics below.

# E(y) confidence interval
conf_interval <- predict(finalModel, interval = "confidence", level = 0.95,
                         newdata = test_data)
conf_interval
confint(finalModel)

# y prediction interval
pred_interval <- predict(finalModel, interval = "prediction", level = 0.95,
                         newdata = test_data)
pred_interval
## create a dataframe to predict certain inputs.


```